DeepSphere: a graph-based spherical CNN

### 2019-09-19 main.tex
update references

Spherical data is common, and comes in two favors: (i) intrinsically spherical, and (ii) projection due to observation.
% spherical data f: S^2 -> R, projection from R^3
Examples of (i) are planetary data (such as meteorological or geological measurements) and brain activity.
Examples of (ii) is the observation of the universe, LIDAR scans, and the digitalization of 3D objects. % through which apparatus?
See \figref{examples}.
In many applications, labels or variables are to be inferred from spherical data.
Examples are the inference of cosmological parameters from the distribution of mass in the universe \citep{perraudin2019deepsphere}, and the segmentation of cyclones from Earth observation \citep{mudigonda2017climateevents}.

@@

This paper focuses on improving the equivariance of \cite{perraudin2019deepsphere}, a scalable graph-based method designed for cosmological applications.
\todo{cite RLGM paper}
Experiments on multiple problems of practical interest shows the competitiveness and flexibility of our method.
Furthermore, those experiments show, contrarily to previously published results \cite{cohen_gauge_2019}, that anisotropic filters may be an unnecessary price to pay.

@@

* HEALPix: improvement from DeepSphere v1 \cite{perraudin2019deepsphere} \\
* equiangular: Renata \& Pascal \\

% \cite{khasanova2017graphomni} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling. They consider the set $\mathcal G$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes the difference in the response to the polynomial spectral filter $\mathcal F = \mathbf L$ evaluated on images of the same object seen at different latitudes. In other words, they solve the minimization problem
% \begin{equation} \label{eq:minimization frossard}
% 	\min_{W\in\mathcal G} \left|\mathcal{F}\left(\mathbf{y}\left(v_{ e}\right)\right)-\mathcal{F}\left(\mathbf{y}\left(v_{ i}\right)\right)\right|
% \end{equation}
% for the adjacency matrix $W$, where $\mathbf y(v_i)$ is the image of the object on the sphere centered on the vertex $v_i$, and $\mathcal F (\mathbf y(v_e))$ is the response of the filter at the vertex $v_e$ that lies at the same longitude of the vertex $v_i$ but on the equator. In their work they prove that the optimal weights solving the minimization problem (\ref{eq:minimization frossard}) are given by weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
% \begin{equation} \label{eq:frossard weights}
% 	w_{ij} = \frac{1}{\norm{x_i-x_j}}
% \end{equation}

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{figure_architecture_v3}
	\caption{Example architecture from \cite{perraudin2019deepsphere}.
		Global tasks need a spatial summarization: the FCN variant is rotation invariant (and accepts inputs of varying sizes), while the CNN variant is not.
		Dense tasks (when the output lives on the sphere, like segmentation) are rotation equivariant.
	}
	\label{fig:architecture}
\end{figure}

@@

% The plan for this section
% 0.1 Explain the sampling problem
\paragraph{Sampling} 
As the graph convolution acts on a sampled version of the signal $\b{f}$ and the rotation on its continuous counterpart $f$, we first need to define a sampling operator.
Given a sampling scheme $V=\{v_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere and a function $f : \mathbb S^2 \supset F_V \to \mathbb R$, the sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \b{f}$ is defined as $\b{f}:\ f_i=f(v_i)$, where $F_V$ suitable subspace of $L^2(\mathbb S^2)$ such that $T_V$ is invertible, i.e., we can unambiguously reconstruct the function $f\in F_V$ from its sampled values $\b{f}$.
The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing \cite{Driscoll:1994:CFT:184069.184073}. 
For most samplings, it is not known if $F_V$ exist and hence if $T_V$ is invertible. A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds, and thus we have a closed form of $T_V^{-1}$ is known. % \cite{Driscoll:1994:CFT:184069.184073}
For sampling schemes where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\bf{f}$, thus approximating $T_V^{-1}$. 
For all theoretical consideration, we assume that $F_V$ exists and $f \in F_V$.

@@

\subsection{Finding a the optimal set of weights}
% !) summary the work of Khasanova -> No! to be put in section 2) Method
\cite{khasanova2017graphomni} designed a Laplacian $\b{L}$ explicitly intended to work with the equiangular sampling. 
They consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude latitude axis.
Their approach leads to weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
\begin{equation} \label{eq:frossard weights}
	w_{ij} = \frac{1}{\norm{x_i-x_j}}
\end{equation}

@@

\begin{table}
    \centering
    \begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed}\\
        \cmidrule(lr){2-3} \cmidrule(lr){4-4} \cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & F1 & mAP & params & inference [ms] & training \\ \hline
        \cite{cohen_spherical_2018} & 78.85 & 67.6 & 1.4M & 38 & 50h\\
        % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
        \cite{esteves_learning_2017} & 79.36 & 68.5 & 500k & 10 & 2h52\\ \hline
        DeepSphere \emph{Equiangular} & 79.36 & 66.5 & 190k & 1 & 50m \\
        DeepSphere \emph{HEALPix} & 80.65 & 68.6 & 190k & 1 & 50m\\
        DeepSphere \emph{Improved HEALPix} & ? & ? & 190k & ? & ?
    \end{tabular}
    \caption{Performance of different models for SHREC'17 task. F1-score computed with sklearn, mAP from the official script of the competition.}
    \label{tab:SHREC17_class}
\end{table}

@@

\begin{table}
	\begin{tabular}{l|c c c c}
	\multicolumn{1}{l}{} & Accuracy & Average Precision & \multicolumn{2}{c}{Speed}\\
	\cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-5}
	\multicolumn{1}{l}{Method} & mean & mean & inference [ms] & training \\ \hline
	%Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
	\cite{jiang_spherical_2019} & 94.67 & - & - & -\\
	\cite{jiang_spherical_2019} \emph{rerun} & 94.95 & 38.41 & 10 & 10h\\
	% 328'339
	\cite{cohen_gauge_2019} (S2R) & 97.5 & 68.6 & - & -\\
	\cite{cohen_gauge_2019} (R2R) & 97.7 & 75.9 & - & -\\ \hline
	% unknown
	DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 33 & 13h \\
	DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 33 & 13h\\
	% 12'926'432
	\end{tabular}
	\caption{Climate pattern segmentation mean accuracy (\%), mean Average Precision (\%) and speed for different models run on the icosahedron dataset from \cite{jiang_spherical_2019}}
\end{table}

@@

\begin{definition}{}(Heat Kernel Graph Laplacian operator)\\
	\label{def:Heat Kernel Graph Laplacian operator}
	\text{Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of the manifold we define the \textbf{operator} }$L_n^t$ such that
	$$L_n^tf(y) := \frac{1}{n}\left[ \sum_{i=0}^{n-1} \exp{-\frac{||x_i-y||^2}{4t}}\left(f(y)-f(x_i)\right)\right]$$
\end{definition}
\begin{definition}{} \cite{Belkin:2005:TTF:2138147.2138189}\\ \label{eq: my L^t} Let $\mu$ be the uniform probability measure on the manifold $\mathcal M$, and let $\text{vol}(\mathcal M)$ be the volume of $\mathcal M$. We define the functional approximation to the Laplace-Beltrami operator to be the operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
	\label{def:Functional approximation to the Laplace-Beltrami operator}
	$$ L^tf(y) = \int_{\mathcal M}e^{-\frac{||y-x||^2}{4t}}\left(f(y)-f(x)\right)d\mu(x)$$
\end{definition}

@@

\begin{prop} \cite{Belkin:2005:TTF:2138147.2138189} \\
Let $\mathcal M$ be a $k$-dimensional compact smooth manifold embedded in some euclidean space $\mathbb R^N$, and fix $p\in\mathcal M$. Let the data points $x_1, \dots, x_n$ be sampled form a uniform distribution on the manifold $\mathcal M$. Set $t_n=n^{-\frac{1}{k+2+\alpha}}$, for any $\alpha>0$ and let $f\in\mathcal C_\infty(\mathcal M)$. Then
	$$\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(p) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\triangle_{\mathcal M}f(p).$$
	\label{prop:3}
\end{prop}

@@

The proof of this result is instructive since it shows that we need to impose some regularity conditions on the sampling. If the sampling is equal area as HEALPix, meaning that all the patches $\sigma_i$ have the same area, then we need to impose that $ d^{(n)}\leq \frac{1}{\sqrt{n}}$. If the sampling is not equal area, meaning that in general $A_i\neq A_j$, it can be shown that we need a slightly more complex condition: $\max_{i=0,\dots,n-1}d_iA_i\leq Cn^{-\frac{3}{2}}$.\\
In the work of Belkin et al. \cite{Belkin:2005:TTF:2138147.2138189} the sampling is drawn form a uniform random distribution on the sphere, and their proof heavily relies on the uniformity properties of the distribution from which the sampling is drawn. In our case the sampling is deterministic, and the fact that for a sphere there doesn't exist a regular sampling with more than 12 points (the vertices of a icosahedron) is indeed a problem that we need to overcome by imposing the regularity conditions above.

To conclude, we can see that the result obtained has the same form than the result obtained in \cite{Belkin:2005:TTF:2138147.2138189}. Given the kernel density $t(n)=n^\beta$, if Belkin et al. proved convergence in the random case for $\beta \in (-\frac{1}{4}, 0)$, we proved convergence in the HEALPix case for $\beta \in (-\frac{1}{5}, 0)$. This kind of result can be interpreted in the following way. In order to have this pointwise convergence, we need to reduce the kernel width but \textit{not so fast} compared to the resolution of the graph. In other words, the kernel width has to be reduced but is somewhat limited by the resolution of the graph. In the next section we'll see how to set in practice a good kernel width $t$ given a graph resolution $n$.
\begin{remark}
	Pointwise convergence is just a necessary condition for spectral convergence.  Theorem \ref{theo:pointwise convergence in the healpix case} does not imply convergence of eigenvalues and eigenvectors.
\end{remark}

@@

\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{4}{c}{Accuracy} & Size\\
        \cmidrule(lr){2-5} \cmidrule(lr){6-6}
        \multicolumn{1}{l}{Method} & TC & AR & BG & mean & params \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang_spherical_2019} & 94 & 93 & 97 & 94.67 & 330k\\
        \cite{jiang_spherical_2019} \emph{rerun} & 93.9 & 95.7 & 95.2 & 94.95 & 330k\\
        % 328'339
        \cite{cohen_gauge_2019} (S2R) & 97.3 & 97.3 & 97.8 & 97.5 & -\\
        \cite{cohen_gauge_2019} (R2R) & 97.8 & 97.4 & 97.9 & 97.7 & -\\ \hline
        DS (weighted) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ & 13M\\
        DS (non-weighted) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ & 13M\\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 97.1 & 97.6 & 96.5 & 97.1 & 590k\\
        DS-Jiang (non-weighted) & 33.6 & 93.6 & 99.3 & 75.5 & 590k\\ \hline
        % 590k
        DS-optimal (weighted) & 91.5 & 93.4 & 99.0 & 94.6 & 52M\\
        DS-optimal (non-weighted) & 73.4 & 92.7 & 99.8 & 88.7 & 52M\\ \hline
        %DS-Cohen (weighted) & 95.5 & 96.9 & 93.9 & 95.4 & 2M \\
        %DS-Cohen (non-weighted) & 95.5 & 96.9 & 93.9 & 95.4 & 2M \\
        % DeepSphere (equi non-weighted) & 31.3 & 75.2 & 99.9 & 68.80
    \end{tabular}
    \caption{Climate pattern segmentation accuracy (\%) for BG, TC
and AR classes plus mean accuracy.}
\end{table}

* DS-jiang is the similar architecture as \cite{jiang_spherical_2019}.\\
* DS-optimal has 2 times the number of feature maps of DS.\\

\begin{table}
\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
        \cmidrule(lr){2-4}\cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & TC & AR & mean & inference [ms] & training \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang_spherical_2019} \emph{rerun} & 11.08 & 65.21 & 38.41 & 10.2 & 10h14m\\
        % 328'339
        \cite{cohen_gauge_2019} (S2R) & - & -& 68.6 & - & - \\
        \cite{cohen_gauge_2019} (R2R) & - & -& 75.9 & - & -\\ \hline
        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 33 & 13h \\
        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 33 & 13h \\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 49.7 & 89.2 & 69.5 & 5 & 3h06m\\
        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 & 5 & 3h04m \\ \hline
        % 590k
        DS-optimal (weighted) & 52.80 & 94.78 & 73.79 & 50 & 20h \\
        DS-optimal (non-weighted) & 84.71 & 98.05 & 91.38 & 50 & 20h \\ \hline
        %DS-Cohen (weighted) & 13.1 & 80.3 & 46.7 & 11 & 4h \\
        % DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
    \end{tabular}
    \caption{Climate pattern segmentation average precision for positive classes and mean as well, plus speed performance for inference (one training pass for one instance)  and training time.}
\end{table}

@@

\cite{khasanova2017graphomni} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling. They consider the set $\mathcal G$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes the difference in the response to the polynomial spectral filter $\mathcal F = \mathbf L$ evaluated on images of the same object seen at different latitudes. In other words, they solve the minimization problem
\begin{equation} \label{eq:minimization frossard}
	\min_{W\in\mathcal G} \left|\mathcal{F}\left(\mathbf{y}\left(v_{ e}\right)\right)-\mathcal{F}\left(\mathbf{y}\left(v_{ i}\right)\right)\right|
\end{equation}
for the adjacency matrix $W$, where $\mathbf y(v_i)$ is the image of the object on the sphere centered on the vertex $v_i$, and $\mathcal F (\mathbf y(v_e))$ is the response of the filter at the vertex $v_e$ that lies at the same longitude of the vertex $v_i$ but on the equator. In their work they prove that the optimal weights solving the minimization problem (\ref{eq:minimization frossard}) are given by weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
\begin{equation} \label{eq:frossard weights}
	w_{ij} = \frac{1}{\norm{x_i-x_j}}
\end{equation}
This construction is interesting since it is adapted to the equiangular sampling, and leads to a very sparse graph with only 4 neighbors per vertex. Furthermore, to obtain the weights (\ref{eq:frossard weights}) every calculation was done in the \textit{spatial domain}, without any consideration about the spectral interpretation of the filter. In order to compare it to the HKGL we show the equivariance error by spherical harmonic degree in figure \ref{fig:Equivariance error of the Frossard-Khasanove graph}. It can be appreciated how this construction performs a little worse that the full HKGL for low bandwidth samplings, but converges faster than the \textit{full} HKGL, and its spectrum looks much more similar to the one of $\Delta_{\mathbb S^2}$.

>>>>

Spherical data is common, and comes in two favors: (i) intrinsically spherical, and (ii) projection due to observation.
% spherical data f: S^2 -> R, projection from R^3
Examples of (i) are planetary data (such as meteorological or geological measurements) and brain activity.
Examples of (ii) is the observation of the universe, LIDAR scans, and the digitalization of 3D objects. % through which apparatus?
See \figref{examples}.
In many applications, labels or variables are to be inferred from spherical data.
Examples are the inference of cosmological parameters from the distribution of mass in the universe \citep{perraudin2019deepspherecosmo}, and the segmentation of cyclones from Earth observation \citep{mudigonda2017climateevents}.

@@

This paper focuses on improving the equivariance of \cite{perraudin2019deepspherecosmo}, a scalable graph-based method designed for cosmological applications.
\todo{cite RLGM paper}
Experiments on multiple problems of practical interest shows the competitiveness and flexibility of our method.
Furthermore, those experiments show, contrarily to previously published results \cite{cohen2019gauge}, that anisotropic filters may be an unnecessary price to pay.

@@

* HEALPix: improvement from DeepSphere v1 \cite{perraudin2019deepspherecosmo} \\
* equiangular: Renata \& Pascal \\

% \cite{khasanova2017sphericalcnn} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling. They consider the set $\mathcal G$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes the difference in the response to the polynomial spectral filter $\mathcal F = \mathbf L$ evaluated on images of the same object seen at different latitudes. In other words, they solve the minimization problem
% \begin{equation} \label{eq:minimization frossard}
% 	\min_{W\in\mathcal G} \left|\mathcal{F}\left(\mathbf{y}\left(v_{ e}\right)\right)-\mathcal{F}\left(\mathbf{y}\left(v_{ i}\right)\right)\right|
% \end{equation}
% for the adjacency matrix $W$, where $\mathbf y(v_i)$ is the image of the object on the sphere centered on the vertex $v_i$, and $\mathcal F (\mathbf y(v_e))$ is the response of the filter at the vertex $v_e$ that lies at the same longitude of the vertex $v_i$ but on the equator. In their work they prove that the optimal weights solving the minimization problem (\ref{eq:minimization frossard}) are given by weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
% \begin{equation} \label{eq:frossard weights}
% 	w_{ij} = \frac{1}{\norm{x_i-x_j}}
% \end{equation}

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{figure_architecture_v3}
	\caption{Example architecture from \cite{perraudin2019deepspherecosmo}.
		Global tasks need a spatial summarization: the FCN variant is rotation invariant (and accepts inputs of varying sizes), while the CNN variant is not.
		Dense tasks (when the output lives on the sphere, like segmentation) are rotation equivariant.
	}
	\label{fig:architecture}
\end{figure}

@@

% The plan for this section
% 0.1 Explain the sampling problem
\paragraph{Sampling}
As the graph convolution acts on a sampled version of the signal $\b{f}$ and the rotation on its continuous counterpart $f$, we first need to define a sampling operator.
Given a sampling scheme $V=\{v_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere and a function $f : \mathbb S^2 \supset F_V \to \mathbb R$, the sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \b{f}$ is defined as $\b{f}:\ f_i=f(v_i)$, where $F_V$ suitable subspace of $L^2(\mathbb S^2)$ such that $T_V$ is invertible, i.e., we can unambiguously reconstruct the function $f\in F_V$ from its sampled values $\b{f}$.
The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing \cite{driscoll1994Fouriersphere}.
For most samplings, it is not known if $F_V$ exist and hence if $T_V$ is invertible. A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds, and thus we have a closed form of $T_V^{-1}$ is known. % \cite{driscoll1994Fouriersphere}
For sampling schemes where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\bf{f}$, thus approximating $T_V^{-1}$.
For all theoretical consideration, we assume that $F_V$ exists and $f \in F_V$.

@@

\subsection{Finding a the optimal set of weights}
% !) summary the work of Khasanova -> No! to be put in section 2) Method
\cite{khasanova2017sphericalcnn} designed a Laplacian $\b{L}$ explicitly intended to work with the equiangular sampling.
They consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude latitude axis.
Their approach leads to weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
\begin{equation} \label{eq:frossard weights}
	w_{ij} = \frac{1}{\norm{x_i-x_j}}
\end{equation}

@@

\begin{table}
    \centering
    \begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed}\\
        \cmidrule(lr){2-3} \cmidrule(lr){4-4} \cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & F1 & mAP & params & inference [ms] & training \\ \hline
        \cite{cohen2018sphericalcnn} & 78.85 & 67.6 & 1.4M & 38 & 50h\\
        % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
        \cite{esteves2018sphericalcnn} & 79.36 & 68.5 & 500k & 10 & 2h52\\ \hline
        DeepSphere \emph{Equiangular} & 79.36 & 66.5 & 190k & 1 & 50m \\
        DeepSphere \emph{HEALPix} & 80.65 & 68.6 & 190k & 1 & 50m\\
        DeepSphere \emph{Improved HEALPix} & ? & ? & 190k & ? & ?
    \end{tabular}
    \caption{Performance of different models for SHREC'17 task. F1-score computed with sklearn, mAP from the official script of the competition.}
    \label{tab:SHREC17_class}
\end{table}

@@

\begin{table}
	\begin{tabular}{l|c c c c}
	\multicolumn{1}{l}{} & Accuracy & Average Precision & \multicolumn{2}{c}{Speed}\\
	\cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-5}
	\multicolumn{1}{l}{Method} & mean & mean & inference [ms] & training \\ \hline
	%Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
	\cite{jiang2019sphericalcnn} & 94.67 & - & - & -\\
	\cite{jiang2019sphericalcnn} \emph{rerun} & 94.95 & 38.41 & 10 & 10h\\
	% 328'339
	\cite{cohen2019gauge} (S2R) & 97.5 & 68.6 & - & -\\
	\cite{cohen2019gauge} (R2R) & 97.7 & 75.9 & - & -\\ \hline
	% unknown
	DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 33 & 13h \\
	DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 33 & 13h\\
	% 12'926'432
	\end{tabular}
	\caption{Climate pattern segmentation mean accuracy (\%), mean Average Precision (\%) and speed for different models run on the icosahedron dataset from \cite{jiang2019sphericalcnn}}
\end{table}

@@

\begin{definition}{}(Heat Kernel Graph Laplacian operator)\\
	\label{def:Heat Kernel Graph Laplacian operator}
	\text{Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of the manifold we define the \textbf{operator} }$L_n^t$ such that
	$$L_n^tf(y) := \frac{1}{n}\left[ \sum_{i=0}^{n-1} \exp{-\frac{||x_i-y||^2}{4t}}\left(f(y)-f(x_i)\right)\right]$$
\end{definition}
\begin{definition}{} \cite{belkin2005towards}\\ \label{eq: my L^t} Let $\mu$ be the uniform probability measure on the manifold $\mathcal M$, and let $\text{vol}(\mathcal M)$ be the volume of $\mathcal M$. We define the functional approximation to the Laplace-Beltrami operator to be the operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
	\label{def:Functional approximation to the Laplace-Beltrami operator}
	$$ L^tf(y) = \int_{\mathcal M}e^{-\frac{||y-x||^2}{4t}}\left(f(y)-f(x)\right)d\mu(x)$$
\end{definition}

@@

\begin{prop} \cite{belkin2005towards} \\
Let $\mathcal M$ be a $k$-dimensional compact smooth manifold embedded in some euclidean space $\mathbb R^N$, and fix $p\in\mathcal M$. Let the data points $x_1, \dots, x_n$ be sampled form a uniform distribution on the manifold $\mathcal M$. Set $t_n=n^{-\frac{1}{k+2+\alpha}}$, for any $\alpha>0$ and let $f\in\mathcal C_\infty(\mathcal M)$. Then
	$$\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(p) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\triangle_{\mathcal M}f(p).$$
	\label{prop:3}
\end{prop}

@@

The proof of this result is instructive since it shows that we need to impose some regularity conditions on the sampling. If the sampling is equal area as HEALPix, meaning that all the patches $\sigma_i$ have the same area, then we need to impose that $ d^{(n)}\leq \frac{1}{\sqrt{n}}$. If the sampling is not equal area, meaning that in general $A_i\neq A_j$, it can be shown that we need a slightly more complex condition: $\max_{i=0,\dots,n-1}d_iA_i\leq Cn^{-\frac{3}{2}}$.\\
In the work of Belkin et al. \cite{belkin2005towards} the sampling is drawn form a uniform random distribution on the sphere, and their proof heavily relies on the uniformity properties of the distribution from which the sampling is drawn. In our case the sampling is deterministic, and the fact that for a sphere there doesn't exist a regular sampling with more than 12 points (the vertices of a icosahedron) is indeed a problem that we need to overcome by imposing the regularity conditions above.

To conclude, we can see that the result obtained has the same form than the result obtained in \cite{belkin2005towards}. Given the kernel density $t(n)=n^\beta$, if Belkin et al. proved convergence in the random case for $\beta \in (-\frac{1}{4}, 0)$, we proved convergence in the HEALPix case for $\beta \in (-\frac{1}{5}, 0)$. This kind of result can be interpreted in the following way. In order to have this pointwise convergence, we need to reduce the kernel width but \textit{not so fast} compared to the resolution of the graph. In other words, the kernel width has to be reduced but is somewhat limited by the resolution of the graph. In the next section we'll see how to set in practice a good kernel width $t$ given a graph resolution $n$.
\begin{remark}
	Pointwise convergence is just a necessary condition for spectral convergence.  Theorem \ref{theo:pointwise convergence in the healpix case} does not imply convergence of eigenvalues and eigenvectors.
\end{remark}

@@

\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{4}{c}{Accuracy} & Size\\
        \cmidrule(lr){2-5} \cmidrule(lr){6-6}
        \multicolumn{1}{l}{Method} & TC & AR & BG & mean & params \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang2019sphericalcnn} & 94 & 93 & 97 & 94.67 & 330k\\
        \cite{jiang2019sphericalcnn} \emph{rerun} & 93.9 & 95.7 & 95.2 & 94.95 & 330k\\
        % 328'339
        \cite{cohen2019gauge} (S2R) & 97.3 & 97.3 & 97.8 & 97.5 & -\\
        \cite{cohen2019gauge} (R2R) & 97.8 & 97.4 & 97.9 & 97.7 & -\\ \hline
        DS (weighted) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ & 13M\\
        DS (non-weighted) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ & 13M\\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 97.1 & 97.6 & 96.5 & 97.1 & 590k\\
        DS-Jiang (non-weighted) & 33.6 & 93.6 & 99.3 & 75.5 & 590k\\ \hline
        % 590k
        DS-optimal (weighted) & 91.5 & 93.4 & 99.0 & 94.6 & 52M\\
        DS-optimal (non-weighted) & 73.4 & 92.7 & 99.8 & 88.7 & 52M\\ \hline
        %DS-Cohen (weighted) & 95.5 & 96.9 & 93.9 & 95.4 & 2M \\
        %DS-Cohen (non-weighted) & 95.5 & 96.9 & 93.9 & 95.4 & 2M \\
        % DeepSphere (equi non-weighted) & 31.3 & 75.2 & 99.9 & 68.80
    \end{tabular}
    \caption{Climate pattern segmentation accuracy (\%) for BG, TC
and AR classes plus mean accuracy.}
\end{table}

* DS-jiang is the similar architecture as \cite{jiang2019sphericalcnn}.\\
* DS-optimal has 2 times the number of feature maps of DS.\\

\begin{table}
\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
        \cmidrule(lr){2-4}\cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & TC & AR & mean & inference [ms] & training \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang2019sphericalcnn} \emph{rerun} & 11.08 & 65.21 & 38.41 & 10.2 & 10h14m\\
        % 328'339
        \cite{cohen2019gauge} (S2R) & - & -& 68.6 & - & - \\
        \cite{cohen2019gauge} (R2R) & - & -& 75.9 & - & -\\ \hline
        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 33 & 13h \\
        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 33 & 13h \\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 49.7 & 89.2 & 69.5 & 5 & 3h06m\\
        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 & 5 & 3h04m \\ \hline
        % 590k
        DS-optimal (weighted) & 52.80 & 94.78 & 73.79 & 50 & 20h \\
        DS-optimal (non-weighted) & 84.71 & 98.05 & 91.38 & 50 & 20h \\ \hline
        %DS-Cohen (weighted) & 13.1 & 80.3 & 46.7 & 11 & 4h \\
        % DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
    \end{tabular}
    \caption{Climate pattern segmentation average precision for positive classes and mean as well, plus speed performance for inference (one training pass for one instance)  and training time.}
\end{table}

@@

\cite{khasanova2017sphericalcnn} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling. They consider the set $\mathcal G$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes the difference in the response to the polynomial spectral filter $\mathcal F = \mathbf L$ evaluated on images of the same object seen at different latitudes. In other words, they solve the minimization problem
\begin{equation} \label{eq:minimization frossard}
	\min_{W\in\mathcal G} \left|\mathcal{F}\left(\mathbf{y}\left(v_{ e}\right)\right)-\mathcal{F}\left(\mathbf{y}\left(v_{ i}\right)\right)\right|
\end{equation}
for the adjacency matrix $W$, where $\mathbf y(v_i)$ is the image of the object on the sphere centered on the vertex $v_i$, and $\mathcal F (\mathbf y(v_e))$ is the response of the filter at the vertex $v_e$ that lies at the same longitude of the vertex $v_i$ but on the equator. In their work they prove that the optimal weights solving the minimization problem (\ref{eq:minimization frossard}) are given by weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
\begin{equation} \label{eq:frossard weights}
	w_{ij} = \frac{1}{\norm{x_i-x_j}}
\end{equation}
This construction is interesting since it is adapted to the equiangular sampling, and leads to a very sparse graph with only 4 neighbors per vertex. Furthermore, to obtain the weights (\ref{eq:frossard weights}) every calculation was done in the \textit{spatial domain}, without any consideration about the spectral interpretation of the filter. In order to compare it to the HKGL we show the equivariance error by spherical harmonic degree in figure \ref{fig:Equivariance error of the Frossard-Khasanove graph}. It can be appreciated how this construction performs a little worse that the full HKGL for low bandwidth samplings, but converges faster than the \textit{full} HKGL, and its spectrum looks much more similar to the one of $\Delta_{\mathbb S^2}$.
